Sharp RDD

### 2024-11-22 methods/diff-in-diff.qmd
Bigger font for slides

did |> 
  group_by(school, year) |> 
  summarize(mean = ggplot2::mean_se(prosocial_index, mult = 1.96)) |> 
  unnest(mean) |> 
  ggplot(aes(x = year, y = y, color = school)) +
  geom_vline(xintercept = 2022.5, linetype = "dashed") +
  geom_line(linewidth = 0.25, show.legend = FALSE) +
  geom_pointrange(aes(ymin = ymin, ymax = ymax)) +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8])) +
  labs(x = NULL, y = "Prosocial index", color = NULL) +
  theme_np()
```

@@

ggplot(treatment_effects, aes(x = Coefficient, y = fct_rev(name))) +
  geom_vline(xintercept = 10, color = clrs$Prism[2]) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high)) +
  labs(x = "Treatment effect", y = NULL) +
  theme_np() +
  theme(panel.grid.major.y = element_blank())
```

>>>>

did |> 
  group_by(school, year) |> 
  summarize(mean = ggplot2::mean_se(prosocial_index, mult = 1.96)) |> 
  unnest(mean) |> 
  ggplot(aes(x = year, y = y, color = school)) +
  geom_vline(xintercept = 2022.5, linetype = "dashed") +
  geom_line(linewidth = 0.25, show.legend = FALSE) +
  geom_pointrange(aes(ymin = ymin, ymax = ymax)) +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8])) +
  labs(x = NULL, y = "Prosocial index", color = NULL) +
  theme_np(base_size = 16)
```

@@

ggplot(treatment_effects, aes(x = Coefficient, y = fct_rev(name))) +
  geom_vline(xintercept = 10, color = clrs$Prism[2]) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high)) +
  labs(x = "Treatment effect", y = NULL) +
  theme_np(base_size = 16) +
  theme(panel.grid.major.y = element_blank())
```

### 2024-11-22 methods/rdd-sharp.qmd
Bigger font for slides

```{r}
ggplot(rdd, aes(x = entrance_score, y = prosocial_index, color = as.logical(experiential_learning))) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(data = filter(rdd, entrance_score <= 75, entrance_score >= 70),
              method = "lm", se = FALSE, linewidth = 2) +
  geom_smooth(data = filter(rdd, entrance_score > 75, entrance_score <= 80),
              method = "lm", se = FALSE, linewidth = 2) +
  geom_vline(xintercept = 75.5) +
  coord_cartesian(xlim = c(65, 85), ylim = c(60, 100)) +
  labs(x = "Entrance test score", y = "Prosocial index", color = "Participated") +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8])) +
  theme_np()
```

@@

ggplot(treatment_effects, aes(x = estimate, y = fct_rev(name))) +
  geom_vline(xintercept = 8.5, color = clrs$Prism[2]) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  labs(x = "Treatment effect", y = NULL) +
  theme_np() +
  theme(panel.grid.major.y = element_blank())
```

>>>>

```{r}
ggplot(rdd, aes(x = entrance_score, y = prosocial_index, color = as.logical(experiential_learning))) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(data = filter(rdd, entrance_score <= 75, entrance_score >= 70),
              method = "lm", se = FALSE, linewidth = 2) +
  geom_smooth(data = filter(rdd, entrance_score > 75, entrance_score <= 80),
              method = "lm", se = FALSE, linewidth = 2) +
  geom_vline(xintercept = 75.5) +
  coord_cartesian(xlim = c(65, 85), ylim = c(60, 100)) +
  labs(x = "Entrance test score", y = "Prosocial index", color = "Participated") +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8])) +
  theme_np(base_size = 16)
```

@@

ggplot(treatment_effects, aes(x = estimate, y = fct_rev(name))) +
  geom_vline(xintercept = 8.5, color = clrs$Prism[2]) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  labs(x = "Treatment effect", y = NULL) +
  theme_np(base_size = 16) +
  theme(panel.grid.major.y = element_blank())
```
